### 2017-11-28 paper/sections/5_file-systems.tex
paper: add to Fig12 to address #48
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}. The policy works
``out-of-the-box", which suggests that data management policies are general and
can be used across domains.
\label{fig:trace-atime}}
\end{figure}

>>>>

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}. A load balancing
policy can use the same pattern detection to make decisions, such as avoiding
migration when the workload is accessing the same subset of keys or keeping
groups of accesses local to a single server.
\label{fig:trace-atime}}
\end{figure}
